$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-02-25 paper/e6ssm-tuning-paper.tex
Updated notation to not use SUGRA-style trilinears
Added 1-loop beta function for A_\lambda (actually T_\lambda is more convenient as that is what is used in the fine tuning code)
Added one-loop beta functions for soft Higgs and singlet masses, defined trace contributions in Appendix as well. Trace contributions also involve charges, this will have to be addressed in the body of the paper

It is sufficient to consider the trilinear coupling $a_\lambda\equiv \lambda A_\lambda$, for which the relevant expressions read

@@

\beta_{a_\lambda}^{(1)}&=,\label{eq:USSMTLambdaBetaOneLoop}\\

@@

b_{a_\lambda}^{(2)}&=.\label{eq:USSMTLambdaOt2Coeff}

>>>>

It is sufficient for our purposes to consider the trilinear coupling $a_\lambda\equiv \lambda A_\lambda$, rather than $A_\lambda$, for which the relevant expressions read

@@

\beta_{a_\lambda}^{(1)}&=2\lambda \left [ 2 \Sigma_{a_\lambda}+3\Sigma_{a_\kappa}+3y_ta_t+3y_ba_b+y_\tau a_\tau+\frac{3}{5}g_1^2M_1+3g_2^2 M_2+2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\right ]\nonumber\\
&{}+a_\lambda \left [ 6\lambda^2+2\Sigma_\lambda+3\Sigma_\kappa+3y_t^2+3y_b^2+y_\tau^2-\frac{3}{5}g_1^2-3g_2^2-2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\right ],\label{eq:USSMTLambdaBetaOneLoop}\\

@@

b_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaOt2Coeff}
&\Sigma_{a_\lambda}=\lambda_1 a_{\lambda_1}+\lambda_2 a_{\lambda_2}+\lambda_3 a_{\lambda_3},\qquad \Sigma_{a_\kappa}=\kappa_1 a_{\kappa_1}+\kappa_2 a_{\kappa_2}+\kappa_3 a_{\kappa_3},\\
&\Pi_{a_\lambda}=\lambda_1^3 a_{\lambda_1}+\lambda_2^3 a_{\lambda_2}+\lambda_3^3 a_{\lambda_3},\qquad \Pi_{a_\kappa}=\kappa_1^3 a_{\kappa_1}+\kappa_2^3 a_{\kappa_2}+\kappa_3^3 a_{\kappa_3},
Note that $a_{\lambda_i}\equiv\lambda_i A_{\lambda_i}$, $a_{\kappa_i}\equiv\kappa_i A_{\kappa_i}$, $a_t\equiv y_t A_t$, $a_b\equiv y_b A_b$ and $a_\tau= y_\tau A_\tau$. Definining 
\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1}\\
\Sigma_1'&=\sum_{i=1}^3\left ( 6\tilde{Q}_Qm_{Qi}^2+3\tilde{Q}_um_{ui}^2+3\tilde{Q}_dm_{di}^2+\tilde{Q}_em_{ei}^2+2\tilde{Q}_Lm_{Li}^2+2\tilde{Q}_2m_{H_{ui}}^2+2\tilde{Q}_1m_{H_{di}}^2\right.\nonumber\\
&\quad{}\left.+\tilde{Q}_Sm_{Si}^2+3\tilde{Q}_{\overline{D}}m_{\overline{D}_i}^2+3\tilde{Q}_Dm_{Di}^2\right )+2\tilde{Q}_{H'}m_{H'}^2+2\tilde{Q}_{\overline{H'}}m_{\overline{H'}}^2,\label{eq:USSMGaugeSigmaTerm1Pr}
the one- and two-loop $\beta$ functions and the $O(t^2)$ coefficients for $m_{H_d}^2$ are
\beta_{m_{H_d}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+6a_b^2\nonumber\\
&{}+2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+2a_\tau^2-6g_2^2 M_2^2-\frac{6}{5}g_1^2 M_1^2-8\tilde{Q}_1^2g_1'^2 M_1'^2\nonumber\\
&{}-\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_1g_1'^2\Sigma_1',\label{eq:USSMmHd2BetaOneLoop}\\
\beta_{m_{H_d}^2}^{(2)}&=,\label{eq:USSMmHd2BetaTwoLoop}\\
b_{m_{H_d}^2}^{(2)}&=.\label{eq:USSMmHd2Ot2Coeff}
Similarly, those for $m_{H_u}^2$ read
\beta_{m_{H_u}^2}^{(1)}&=2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+2a_\lambda^2+6y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+6a_t^2\nonumber\\
&{}-6g_2^2M_2^2-\frac{6}{5}g_1^2M_1^2-8\tilde{Q}_2^2g_1'^2M_1'^2+\frac{3}{5}g_1^2\Sigma_1+2\tilde{Q}_2g_1'^2\Sigma_1',\label{eq:USSMmHu2BetaOneLoop}\\
\beta_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2BetaTwoLoop}\\
b_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2Ot2Coeff}
while those for $m_S^2$ are
\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\
&{}-8\tilde{Q}_S^2g_1'^2M_1'^2+2\tilde{Q}_Sg_1'^2\Sigma_1',\label{eq:USSMms2BetaOneLoop}\\
\beta_{m_S^2}^{(2)}&=,\label{eq:USSMms2BetaTwoLoop}\\
b_{m_S^2}^{(2)}&=.\label{eq:USSMms2Ot2Coeff}
